Attack Graph Generation for Microservice Architecture

### 2018-09-24 paper_own_docker/chapters/conclusion.tex
last round of fixes

Microservices are a promising architectural style that advocate practitioners to build systems as a group of small connected  services. Although this style enables better scalability and faster deployment, the full container-based automation within this style raises many security concerns. In this paper, we proposed to use automated attack graph generation as part of the practices of developing microservice-based architectures. Attack graphs aid the developers in identifying attack paths that consist of multiple vulnerability exploitation in the deployed services. The manual constriction of attack graphs is an error-prone, resource consuming activity, hence, automating this construction does not only guarantee efficient construction but also complies with the spirit of DevOps practices. We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big microservice-based systems.

>>>>

Microservices are a promising architectural style that advocate practitioners to build systems as a group of small connected  services. Although this style enables better scalability and faster deployment, the full container-based automation within this style raises many security concerns. In this paper, we proposed to use automated attack graph generation as part of the practices of developing microservice-based architectures. Attack graphs aid the developers in identifying attack paths that consist of multiple vulnerability exploitation in the deployed services. The manual construction of attack graphs is an error-prone, resource consuming activity. Hence, automating this process does not only guarantee efficient construction but also complies with the spirit of DevOps practices. We have shown that such automation, extending previous works in computer networks field, is efficient and scales to complex and big microservice-based systems.

### 2018-09-24 paper_own_docker/chapters/method.tex
last round of fixes

The generator is developed and tested for Docker 17.12.1-ce, and Docker Compose 1.19.0 \cite{merkel2014docker}. Docker Compose\footnote{\url{https://docs.docker.com/compose/}} is a tool for defining the orchestration of  multi-container applications. It provides a static configuration file that specifies the system containers, networks, and ports. Clair and ClairCtl \footnote{\url{https://github.com/coreos/clair}}  are used for vulnerabilities scanning. The generator is written in Python 3.6. Although we used  specific versions of the tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners and microservice architectures by replacing.

@@

In the majority of cases, for an application to be useful, it communicates with the outside world, i.e., it has endpoints that can be used by the outer network. In Docker, this is usually done by using publishing ports. This is the case in both computer networks, as well as in microservice architectures.

@@

In the preprocessing step, we use Clair to generate the vulnerabilities of a given image. Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing \textit{CVE-ID}, a description and attack vector for each vulnerability. An attack vector is an entity that describes which conditions and effects are connected to this vulnerability. We collect the fields in the attack vector which are,  as defined by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete). Unfortunately, Clair does not provide a command line interface to analyze a Docker image. We use another tool, i.e.,  Clairctl  to analyze a complete Docker image.

@@

After the topology  is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation. Here, we first pre-process the vulnerabilities and convert them into sets of pre- and postconditions. In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules. When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule. An example precondition attack rule would be for a vulnerability to have either "gain root", "gain unrestricted, root shell access" or "obtain root" in its description and all of the Impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" in order to gain the precondition OS(ADMIN) \cite{aksu2018automated}. If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions. If no rule matches, we take None as a precondition and ADMIN(OS) as a postcondition. This results in a list of container vulnerabilities with their preconditions and postconditions.

>>>>

The generator is developed and tested for Docker 17.12.1-ce, and Docker Compose 1.19.0 \cite{merkel2014docker}. Docker Compose\footnote{\url{https://docs.docker.com/compose/}} is a tool for defining the orchestration of  multi-container applications. It provides a static configuration file that specifies the system containers, networks, and ports. Clair and ClairCtl \footnote{\url{https://github.com/coreos/clair}}  are used for vulnerabilities scanning. The generator is written in Python 3.6. Although we used  specific versions of the tools, the pipe and filter structure of the generator can be easily extended to other versions of Docker-Compose, vulnerability scanners, and microservice architectures.

@@

In the majority of cases, for an application to be useful, it communicates with the outside world, i.e., it has endpoints that can be used by the outer network. In Docker, this is usually done by  publishing ports. This is the case in both computer networks, as well as in microservice architectures.

@@

In the preprocessing step, we use Clair to generate the vulnerabilities of a given image. Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing \textit{CVE-ID}, a description and attack vector for each vulnerability. An attack vector is an entity that describes which conditions and effects are connected to this vulnerability. We collect the fields in the attack vector which are,  as defined by the National Vulnerability Database(NVD) \cite{booth2013national}, Access Vector (Local, Adjacent Network and Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete) and Availability Impact (None Partial, Complete). Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl  to analyze a complete Docker image.

@@

After the topology  is extracted and the vulnerabilities for each container are generated, we continue with the attack graph generation. Here, we first pre-process the vulnerabilities and convert them into sets of pre- and postconditions. In order to do this, we match the attack vectors acquired earlier from the vulnerability database and keywords of the descriptions of each vulnerability to generate attack rules. When a subset of attack vector fields and description keywords matches a given rule, we use the pre- or postcondition of that rule. An example of a precondition attack rule would be for a vulnerability to have either "gain root", "gain unrestricted, root shell access" or "obtain root" in its description and all of the impacts from the NVD attack vector \cite{booth2013national} to be "COMPLETE" in order to gain the precondition OS(ADMIN) \cite{aksu2018automated}. If more than one rule matches, we take the one with the highest privilege level for the preconditions and the lowest privilege level for the postconditions. If no rule matches, we take None as a precondition and ADMIN(OS) as a postcondition. This results in a list of container vulnerabilities with their preconditions and postconditions.
